

Electroweak precision observables (EWPO) measured at LEP and SLD at the Z-Pole provide still today the backbone of the interpretation of measurements in the electroweak sector. An comprehensive overview is given in~\ref{lepsld05}.    
It is possible to run the ILC at the $Z$ boson pole at 91~GeV.   This
program, at an instantaneous luminosity of  $0.7\cdot10^{34}$ , would provide  about $0.2\,{\rm ab^{-1}}$ in a 1-year run equivalent to about 200 times more than what has been collected at LEP by all four experiments, improving thus in first approach the precision of measurements of electroweak observables by one order of magnitude.  In this section, we describe this program and its projected results. 
A central precision observable is the effective weak mixing angle $\sin\theta_{eff.}$. Note that the most precise measurements at LEP and SLD of the effective weak mixing angle differ by about 3 standard deviations. At a linear collider with polarised beams the effective weak mixing can be extracted in several ways but notably by measuring the left right asymmetry $A_{LR}$. In this case we can make full use of the hadronic decays of the $Z$ with only little sensitivity to experimental effects such as detector acceptance or beam energy measurements. The branching ratio to hadrons is about 20 times higher than that to e.g. muons. Therefore the larger versatility of the linear collider compensates largely for the lower luminosity available at linear colliders compared with circular colliders. 
For individual fermion asymmetries it is instructive to recall how polarisation increases the analysis power of an asymmetry measurement. It is \begin{equation}
A^{0,f}_{FB} = \frac{3}{4}\frac{({\cal A}_e - {\cal P}_e){\cal A}_f}{(1-{\cal P}_e{\cal A}_e)} =  \frac{3}{4} A_P {\cal A}_f  
\end{equation} 
with $A_P$ being the analysis power. It is $A_P\approx 0.85$ for ${\cal P}_e = -0.8$, $A_P\approx 0.74$ for ${\cal P}_e = 0.8$ and $A_P = {\cal A}_e \approx 0.15$ for ${\cal P}_e = 0$.
It follows that already the measurement for individual beam polarisations lead to an increase in sensitivity between 5 and 6.5 compared to the non-polarised case.    
It is finally 
\begin{equation}
A^{0,f}_{FB,LR} = \frac{3}{4} {\cal P}_e {\cal A}_f
\label{eq:afblr}
\end{equation}
The different approaches will allow us to either combine the measurements into one single quantity as in Eq.~\ref{eq:afblr} or look with already high precision at the individual results. The individual results may have different systematics as e.g. migrations in the polar angle spectra are less important in case of right handed electron beams.  
This means that the effective luminosity for asymmetries at the GigaZ is of the order of 6000 times higher than at LEP. Statistical errors go therefore down by a factor of about 80 and therefore well below the per mille level for the corresponding quantities. This puts the systematic errors into the focus. The linear collider requires the control of the beam polarisation. A running at Z Pole may require the introduction of a conventional $e^+$ source, which would exclude the application of the Blondel scheme and require a precise calibration of the polarimeters. The ILC will be run at higher energies at which the process $e^+e^- \rightarrow WW$ will be available. This process will allow for calibrating the polarimeters to a high precision such that a precision of the knowledge of the polarisation of 0.1\% seems to be well in reach. The control of the other systematics that are discussed in LEPSLD-REPORT will benefit from the progress on detectors and theory and can thus be neglected in first order compared with the polarisation. HOWEVER, CHECK INFLUENCE OF BEAM ENERGY. Tab.~\ref{tab:gigazresults} lists the precision of observables as relevant for the Higgs fit. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table*}[tb]
\begin{footnotesize}
  \begin{center}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
      \hline
      Quantity & $\fonevA$ & $\fonevZ$  & $ \foneaZ$  & $\ftwovA$ & $\ftwovZ$ & $\glA$ &   $\grA$ & $\glZ$  & $\grZ$ \\ 
      \hline
      \hline
      %$-100\%,+100\%$  &0.317 & 0.308 &1.7 \\ \cline
       SM Value at tree level & 2/3 &  0.230 & -0.595 & 0 & 0 & 2/3 & 2/3  & 0.824 & -0.364 \\ 
      \hline
       Standard deviation      & 0.002 &  0.003 & 0.007 & 0.001 & 0.002  & 0.005 & 0.005 & 0.008 & 0.009 \\ 
      \hline
      Relative precision [\%] & 0.3 &  0.9 & 1.2  & - & - & 0.8 & 0.8 & 1.0 & 2.5 \\ 
      \hline
      %$+100\%,-100\%$& 0.433 & 0.442 & 1.9\\ \hline
      %$+0.8,-0.3$& 0.63 & 1.3\\ \hline
    \end{tabular}
  \end{center}
  \caption{\sl Standard deviations and resulting relative precisions of form factors and couplings derived from the statistical precisions on the observables cross section and $\afbt$ as listed in Table~\ref{tab:resafb}.}
  \label{tab:gigazresults}
\end{footnotesize}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

